this is for the result part of the draft

### 2017-04-03 analysis/draft.Rmd
Files commited by wflow_commit.

>>>>

```{r}
dat = read.table('../data/GTExColors.txt', sep = '\t', comment.char = '')
colordata = dat[c(1:6,9:18,21:23,26:30,32,33,35,36,38:53),1:2]
# barplot(rep(1, nrow(dat)), col = as.character(dat[,2]))
# just plot for loadings
plot.factor = function(Y,g,k = 1,loading_label = FALSE,color.fill = NULL){
  library(ggplot2)
  N = dim(Y)[1]
  P = dim(Y)[2]
  sample_name = row.names(Y)
  variable_name = colnames(Y)
  # plot the expectation of PVE 
  ssY = sum(Y^2)
  K = dim(g$l)[2]
  pve = (sapply(seq(1,K),function(x){ sum(g$l[,x]^2 %*% t(g$f[,x]^2)) }))/ssY
  pve_dat = data.frame(index = seq(1,K),EPVE = pve)
  plot_pve <- ggplot(pve_dat, aes(index, EPVE)) + geom_point(size = 4)  + geom_line(linetype = "dotdash")

  # plot the loadings
  if(loading_label == TRUE){
    plot_l = plot_factor(g$l[,k],pve[k],N,k,f_lables = row.names(Y),y_lab = "loading values",color.fill = color.fill)
  }else{
    plot_l = plot_factor(g$l[,k],pve[k],N,k,f_lables =NA,y_lab = "loading values",color.fill = color.fill)
  }
  return(list(plot_pve = plot_pve,plot_l = plot_l))
}

#' plot_f
#'
#' plot the factor 
#' @return list of factor, loading and variance of noise matrix
#'  \itemize{
#'   \item{\code{plot_f}} {is a ggplot object for the factors}
#'  }
#' @param f factor to plot
#' @param pve pve for this factor
#' @param P the lenght of this factor
#' @param k the order of the factor
#' @param f_lables the lables for the factor 
#' @param y_lab is the name of the Y axis
#' @details plot_f is to plot the factor as barplot.
#'
#' @importFrom ggplot2 ggplot
#'

plot_factor = function(f,pve,P,k,f_lables = NA,y_lab = "factor values",color.fill = NA){
  library(ggplot2)
  if(any(is.na(f_lables))){
    f_dat <- data.frame(variable = 1:P, Factor = f,
                      sign.f = factor(sign(f)),
                      hjust = factor(sign(f)))

    plot_f = ggplot(f_dat,aes(x = variable,y = Factor,fill = factor(variable))) +
      geom_bar(stat = "identity",width = 0.5,color = "black") +
      scale_fill_manual(values=color.fill) + theme(legend.position="none") +
      labs(title = paste("factor",k,"with PVE=",round(pve,3)), y = y_lab ,x = "index")
  }else{
    f_dat <- data.frame(variable = 1:P, Factor = f,
                      sign.f = factor(sign(f)),
                      variablenames = f_lables,
                      hjust = factor(sign(f)))

    # 120% lim 
    range_f = max(f) - min(f)
    upper_f = max(f,0) + 0.15 * range_f
    lower_f = min(f,0) - 0.15 * range_f

    plot_f = ggplot(f_dat,aes(x = factor(variable),y = Factor,fill = factor(variable))) +
      geom_bar(stat = "identity",width = 0.5,color = "black") +
      scale_fill_manual(values=color.fill) + theme(legend.position="none") +
      geom_text(size = 2.75,angle = 90,hjust = as.character(f_dat$hjust),
                nudge_y = sign(f_dat$Factor) * 0.1 * mean(abs(f_dat$Factor)) ) +
      ylim(lower_f,upper_f) +
      labs(title = paste("factor",k,"with PVE=",round(pve,3) ), y = y_lab,x = "index")
  }
  return(plot_f)
}
load("../data/GTExdata/bflashvarcol.rds")
load("../data/GTExdata/gtexEQTL_zscore.rds")
plot.factor(Y = t(zscore),g = b_flash,k = 1,loading_label = FALSE,color.fill = as.character(colordata[,2]))

# plot_f = ggplot(f_dat,aes(x = factor(variable),y = Factor,color = factor(variable))) +
#       geom_bar(stat = "identity",width = 0.5,fill = "white") +
#       scale_color_manual(values=color.fill) + theme(legend.position="none")

# ggplot(f_dat,aes(x = factor(variable),y = Factor,fill = factor(variable))) +
#       geom_bar(stat = "identity",width = 0.5,color = "black") +
#       scale_fill_manual(values=color.fill) + theme(legend.position="none")
